Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass

### 2025-07-24 paper/paper_accepted_crossref_supp.Rmd
separate supp materials

---
title: "Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass"
author: 
  - Timothy J. Miller^1^^,2^
  - Kiersten L. Curti^1^^,3^
  - Alexander C. Hansell^1^^,4^
# date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: no
    number_sections: yes
    fig_caption: yes
    includes:
      in_header: options_main_final.sty
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
bibliography: bsb-wham.bib
---

@@

We used a development version ([commit 53e236b](https://github.com/timjmiller/wham/tree/53e236b)) of the WHAM package after the release of version 2.0 for all results. All code for fitting models and generating results can be found at [github.com/timjmiller/multi_wham_bsb](https://github.com/timjmiller/multi_wham_bsb).

@@

As described in the methods section, all data and code for conducting analyses and creating the manuscript are available at [DOI].

>>>>

---
title: "Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass"
author: 
  - Timothy J. Miller^1^^,2^
  - Kiersten L. Curti^1^^,3^
  - Alexander C. Hansell^1^^,4^
# date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: no
    number_sections: yes
    fig_caption: yes
    includes:
      in_header: options_accepted_crossref_supp.sty
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
bibliography: bsb-wham.bib
link-citations: yes
---

@@

We used a development version ([commit 53e236b](https://github.com/timjmiller/wham/tree/53e236b)) of the WHAM package after the release of version 2.0 for all results. All code for fitting models and generating results can be found at [github.com/timjmiller/multi_wham_bsb](https://github.com/timjmiller/multi_wham_bsb), which is permanently archived at [doi:10.5281/zenodo.15785564](https://doi.org/10.5281/zenodo.15785564).

@@

As described in the methods section, all data and code for conducting analyses and creating the manuscript are available at [doi:10.5281/zenodo.15785564](https://doi.org/10.5281/zenodo.15785564).
